comgen-outline

### 2017-08-11 paper/comgen-paper.Rmd
edits to formal view section

Particular statements can be made about objects, events, and causes (e.g., "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind.").
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).

>>>>

Particular statements can be made about objects, events, and causes. For example:

1. My dog is friendly. (object)
2. John ran this afternoon. (event)
3. My grandfather drank moonshine and it made him go blind. (cause)

Particular statements refer to individuals of a category of which generalizatons can be made. For example,

4. Dogs are friendly
5. John runs
6. Drinking moonshines makes you go blind

That is, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
